A Real-Time Sonar Simulator for Automatic Target Recognition

### 2016-01-07 Simulator/article.tex
la2pdf commit - 2016:01:07	09:19:40	(to. 7.jan.)

@@

We have developed a synthetic aperture sonar (SAS) simulator that avoids this problem by running sufficiently fast to create templates adapted to the actual scene as part of the classification process. This is achieved with the aid of the massive computing power in graphics processing units (GPUs) and optimized software libraries for scene rendering. The simulator loads a 3D model of the seafloor and an object class model into OpenGL, where emitted sound waves are modeled with a light tube extending all the way down the propagation path of the AUV. We assume rough, isotropic surfaces reflecting sound energy equally in all directions. This can be modeled with a Lambertian scattering model~\cite{Blake1993,Bell1995}, where the intensity of the backscattered sound solely depends on the incidence angle of the transmitted signal onto the model surface. The OpenGL rendering produces an optical 2D intensity image and depth map that reveals the distance from each pixel to the propagation axis. For maximum flexibility this data is finally combined with OpenCL to produce the image templates.

@@

To avoid this problem we have developed a very fast side-looking sonar simulator that generates templates adapted to the actual scene.

synthetic aperture sonar (SAS)

>>>>

% - Adapt simulation to its behaviour, see if they still match.

@@

We have developed a synthetic aperture sonar (SAS) simulator that avoids this problem by running sufficiently fast to create templates adapted to the actual scene as part of the classification process. This is achieved with the aid of the massive computing power in graphics processing units (GPUs) and optimized software libraries for scene rendering. The simulator loads a 3D model of the seafloor and object class into OpenGL and positions the camera at the sonar location. The scene is highlighted using a light tube that extends to infinity along the AUV's axis of probagation. We assume rough, isotropic surfaces reflecting sound energy equally in all directions. This can be modeled with a Lambertian scattering model~\cite{Blake1993,Bell1995}, where the intensity of the backscattered sound solely depends on the incidence angle of the transmitted signal onto the model surface. The OpenGL rendering produces an optical 2D intensity image and depth map that reveals the distance from each pixel to the propagation axis. For maximum flexibility this data is finally combined with OpenCL to produce the image templates.

@@
